---
title: "adlib_graphs"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
 


#counties within state by provider densities (top five) 
#counties within state by provider densities (bottom five)
#counties within a state by provider number (top five) 
#counties within a state by provider number (bottom five)
#counties within state by provider densities by taxonomy (top five) 
#counties within state by provider densities by taxonomy (bottom five)
#counties within a state by provider number by taxonomy (top five) 
#counties within a state by provider number by taxonomy (bottom five) 


```{r}
#counties within state by provider densities (top five) 
```{r}

#these will need to be filled in once we have the actual fuunctions done
PROVIDERDENSBYCTY <- listofproviderdensities
group_by(CTY) %>%
count() %>%
arrange(n)

plot<-ggplot(number_practices.low, aes(x=factor(n), y=nn))+
  geom_bar(stat="identity") + labs(x = "Number of providers", y = "Number of zip codes")
plot
```

#counties within state by provider densities (bottom five)

```{r}
number_practices<-countbyzip %>%
  select(n) %>% #selecting and grouping by frequency
  group_by(n) %>%
  count() %>%
  arrange(n) #arranging by frequency
number_practices.low <- head(number_practices) #getting the first rows of the number_pratices and desingnating them as low numbers of practices

#add axis names
plot<-ggplot(number_practices.low, aes(x=factor(n), y=nn))+
  geom_bar(stat="identity") + labs(x = "Number of providers", y = "Number of zip codes")
plot
```
