---
title: "adlib_graphs"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
 


#counties within state by provider densities (top five) 
#counties within state by provider densities (bottom five)
#counties within a state by provider number (top five) 
#counties within a state by provider number (bottom five)
#counties within state by provider densities by taxonomy (top five) 
#counties within state by provider densities by taxonomy (bottom five)
#counties within a state by provider number by taxonomy (top five) 
#counties within a state by provider number by taxonomy (bottom five) 



#counties within state by provider densities (top five) 
```{r}

#these will need to be filled in once we have the actual functions done
countyproviderdensityhigh <- function(state) {
providersbycountydens <- listofproviderdensities %>%
filter(STATE = state) %>%
group_by(CTY) %>%
count() %>%
arrange(n)
providersbycounty.high <- head(providersbycounty, 5)

plot<-ggplot(providersbycounty.high, aes(x=factor(n), y=nn))+
  geom_bar(stat="identity") + labs(x = "County", y = "Provider density")
plot

}
```

#counties within state by provider density (bottom five)

```{r}
countyproviderdensityhigh <- function(state) {
providersbycountylow <- listofproviderdensities %>%
filter(STATE = state) %>%
group_by(CTY) %>%
count() %>%
arrange(desc = TRUE)
providersbycounty.low <- head(providersbycountylow, 5)

plot<-ggplot(providersbycounty.low, aes(x=factor(n), y=nn))+
  geom_bar(stat="identity") + labs(x = "County", y = "Provider density")
plot

}
```

#counties within a state by provider number (top five) 

```{r}
countyprovidernumberhigh <- function(state) {
providersbycountynumhigh <- listofprovidernumbers %>%
filter(STATE = state) %>%
group_by(CTY) %>%
count() %>%
arrange(desc = TRUE)
providersbycountynum.high <- head(providersbycountynumhigh, 5)

plot<-ggplot(providersbycountynum.high, aes(x=factor(n), y=nn))+
  geom_bar(stat="identity") + labs(x = "County", y = "Number of providers")
plot

}
```


#counties within a state by provider number (bottom five) 

```{r}
countyprovidernumberlow <- function(state) {
providersbycountynumlow <- listofprovidernumbers %>%
filter(STATE = state) %>%
group_by(CTY) %>%
count() %>%
arrange()
providersbycountynum.low <- head(providersbycountynumlow, 5)

plot<-ggplot(providersbycountynum.low, aes(x=factor(n), y=nn))+
  geom_bar(stat="identity") + labs(x = "County", y = "Number of providers")
plot

}
```

#counties within state by provider densities by taxonomy (top five) 
```{r}
countyproviderdensityhigh <- function(state, taxonomy) {
providersbycountydens <- listofproviderdensities %>%
filter(STATE = state) %>%
filter(taxonomy = "taxonomy")
group_by(CTY) %>%
count() %>%
arrange(n)
providersbycounty.high <- head(providersbycounty, 5)

plot<-ggplot(providersbycounty.high, aes(x=factor(n), y=nn))+
  geom_bar(stat="identity") + labs(x = "County", y = "Provider density")
plot

}


```

#counties within state by provider densities by taxonomy (bottom five) 


```{r}
countyproviderdensityhigh <- function(state, taxonomy) {
providersbycountylow <- listofproviderdensities %>%
filter(STATE = state) %>%
filter(taxonomy = taxonomy)
group_by(CTY) %>%
count() %>%
arrange(desc = TRUE)
providersbycounty.low <- head(providersbycountylow, 5)

plot<-ggplot(providersbycounty.low, aes(x=factor(n), y=nn))+
  geom_bar(stat="identity") + labs(x = "County", y = "Provider density")
plot

}
```
