---
title: "Compiled Pull Code"
author: "Alex, Meghan, Jackie, Kari"
date: "November 28, 2018"
output: pdf_document
---

##Background
In general,it can be difficult to find a mental health care provider that meets your needs. There are many different designations of mental health care providers and sometimes, it can be difficult to find the right type of provider. The goal of this project was to gather all the health care providers in Rhode Island, and determine the number of providers by ZIP code, with an emphasis on mental health providers.

##The Data
We used the National Plan and Provider Enumeration System National Provider Identifier (NPI) database to find medical providers. We included all Rhode Island ZIP codes when iterating through the NPI database. We wrote a function to search through the database using all zipcodes in Rhode Island to create a table of all providers. From there, the program sorts through provider taxonomies to select providers that we designated as mental health providers.

##The graphs
The first graph shows. all zip codes and the number of providers in each one.

The second bar graph breaks down how many mental health care providers are in different ZIP codes, from 1 to 11 providers. From this, we learned that there are four ZIP codes with only 1 provider, 6 ZIP codes with two providers, and on the other side, there is only one ZIP code with 11 providers. Note that ZIP codes with 0 providers are not represented in any of these graphs.

The next two graphs show the number of any type of provider, not limited to mental health providers.

The scatter plot shows the number of providers in each RI ZIP code. We can see that most ZIP codes have few providers, with three outliers having more than 1,000 providers. We postulate that these ZIP codes are likely located in major cities.

The final graph shows the number of providers in the top six specialties. We can see that clinical social work is the most common specialty, followed by internal medicine and physical therapy.

```{r setup, include=FALSE}
options(scipen = 3, digits = 3)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(error = TRUE)
knitr::opts_chunk$set(warning=FALSE)
knitr::opts_chunk$set(message=FALSE)
knitr::opts_chunk$set(cache=T)
knitr::opts_chunk$set(collapse=T)
```

```{r}
library(rvest)
library(httr)
library(dplyr)
library(jsonlite)
library(XML)
library(stringr)
library(zipcode)
library(dplyr)
library(stringr)
library(ggplot2)
```

```{r}
#getting zipcode package
library(zipcode)
data(zipcode)
zip.ri <- filter(zipcode,state=="RI")$zip #restricting to RI zip codes
zip.ri <- as.vector(zip.ri)
zip.ri<-zip.ri
```


```{r}
#looping over zip codes and pages when there are more than 100 providers per zip code
#older function not neccesary

NPIcode<-function(zipcode){
  url1<- "https://npiregistry.cms.hhs.gov/registry/search-results-table?addressType=ANY&postal_code=" #setting the url to scrape from
  provider.data <- data.frame() #initializing an empty data frame
  skips <- seq(0,999999999,100) #create skips
  for (i in 1:length(zipcode)) { #iterating over all RI zip codes
    for (j in 1:length(skips)){ #also iterating over skils
      zip <- zipcode[i]
      skip <- skips[j]
  url<-paste0(url1,zip,"&skip=",skip) #pasting the url, with the rhode island zip code and including the skips
  #text scrape to pull our places by zip code
  h <- read_html(url, timeout = 200)
  reps <- h %>% #setting up the repeating structure
     html_node("table") %>%
     html_table()
    if (any(is.na(reps[,1])) | all(is.na(reps[,1]))) { #if the page has no physicians, move to next zip code
    break}
  reps$zip <- zipcode[i]
  provider.data <- rbind(provider.data,reps) #binding together the provider data and reps data
    }
  }
   colnames(provider.data) <- c("NPI","Name","NPI_Type","Primary_Practice_Address","Phone","Primary_Taxonomy","zipcode")
  return(provider.data)
}

provider.data <- NPIcode(zip.ri)
```

```{r}
#old function, do not use 
NPIcode_taxonomy<-function(zipcode,taxonomy){
  url1<- "https://npiregistry.cms.hhs.gov/registry/search-results-table?addressType=ANY&postal_code=" #setting the url to scrape from
  provider.data <- data.frame() #initializing an empty data frame
  skips <- seq(0,9999999,100) #create skips
  for (i in 1:length(zipcode)) { #iterating over all RI zip codes
    for (j in 1:length(skips)){ #also iterating over skils
      zip <- zipcode[i]
      skip <- skips[j]
      tax <- str_replace_all(taxonomy," ","+")
  url<-paste0(url1,zip,"&skip=",skip,"&taxonomy_description=",tax) #pasting the url, with the rhode island zip code and including the skips
  #text scrape to pull our places by zip code
  h <- read_html(url, timeout = 200)
  reps <- h %>% #setting up the repeating structure
     html_node("table") %>%
     html_table()
    if (any(is.na(reps[,1])) | all(is.na(reps[,1]))) { #if the page has no physicians, move to next zip code
    break}
  reps$zip <- zipcode[i]
  provider.data <- rbind(provider.data,reps) #binding together the provider data and reps data
    }
  }
   colnames(provider.data) <- c("NPI","Name","NPI_Type","Primary_Practice_Address","Phone","Primary_Taxonomy","zipcode")
  return(provider.data)
}

provider.data <- NPIcode_taxonomy(zip.ri,"Primary Care")
```


```{r}
providernames <- c("Psychologist Addiction (Substance Use Disorder)", "Counselor Mental Health",  "Psychiatry & Neurology Psychiatry", "Social Worker Clinical", "Counselor Mental Health", "Counselor", "Psychologist Clinical", "Psychologist", "Marriage & Family", "Therapist", "Social Worker", "Clinic/Center Adult Mental Health") #creating a vector of types of provider taxonomies

filteredtable <- filter(provider.data,Primary_Taxonomy %in% providernames) #creating a filtered dataset by provider taxonomies
```


```{r}
countbyzip <- provider.data %>% #creating a count of practices by zip code
group_by(zipcode) %>% 
count() %>%
arrange(n) 

#countbyzip
#create a bar graph of providers by frequency
plot<-ggplot(countbyzip, aes(x=zipcode, y=n))+
  geom_bar(stat="identity")
plot

#number of counties with 1 provider, 2 providers, etc

number_practices<-countbyzip %>%
  select(n) %>% #selecting and grouping by frequency
  group_by(n) %>%
  count() %>%
  arrange(n) #arranging by frequency
number_practices.low <- head(number_practices) #getting the first rows of the number_pratices and desingnating them as low numbers of practices

#add axis names
plot<-ggplot(number_practices.low, aes(x=factor(n), y=nn))+
  geom_bar(stat="identity") + labs(x = "Number of providers", y = "Number of zip codes")
plot
```

```{r}
#Graphs of Provider Type
provider_grouping<-provider.data %>% #creating a count of practices by providers
group_by(Primary_Taxonomy) %>% 
count() %>%
arrange(desc(n)) 
#provider_grouping

#general scatter of all providers types
provider_scatter<-ggplot(provider_grouping, aes(x=Primary_Taxonomy, y=n))+
 geom_point()+
    theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  labs(x = "Provider Types", y = "Number of providers")+
  scale_color_brewer(palette="Set1")
provider_scatter

#create a bar graph of top 5 providers by frequency
top5providers<-head(provider_grouping)
providers_bar<-ggplot(top5providers, aes(x=Primary_Taxonomy, y=n))+
  geom_bar(stat="identity")+
  theme(axis.text.x = element_text(angle=90))+
  labs(x = "Provider Type", y = "Number of Providers")
providers_bar

```


```{r}
#problem: no way to get county from these codes, maybe from this data? https://www.unitedstateszipcodes.org/zip-code-database/
county_collect_NPIcode_taxonomy<-function(county,taxonomy){
  url1<- "https://npiregistry.cms.hhs.gov/registry/search-results-table?addressType=ANY&postal_code=" #setting the url to scrape from
  provider.data <- data.frame() #initializing an empty data frame
  skips <- seq(0,9999999,100) #create skips
  for (i in 1:length(county)) { #iterating over all counties
    for (j in 1:length(skips)){ #also iterating over skils
      county_index <- county[i]
      skip <- skips[j]
      tax <- str_replace_all(taxonomy," ","+")
  url<-paste0(url1,count_index,"&skip=",skip,"&taxonomy_description=",tax) #pasting the url, with the county and including the skips
  #text scrape to pull our places by county
  h <- read_html(url, timeout = 200)
  reps <- h %>% #setting up the repeating structure
     html_node("table") %>%
     html_table()
    if (any(is.na(reps[,1])) | all(is.na(reps[,1]))) { #if the page has no physicians, move to next county
    break}
  reps$county <- county[i]
  provider.data <- rbind(provider.data,reps) #binding together the provider data and reps data
    }
  }
   colnames(provider.data) <- c("NPI","Name","NPI_Type","Primary_Practice_Address","Phone","Primary_Taxonomy","zipcode")
  return(provider.data)
}
provider.data<-NPIcode_taxonomy("02906", "Mental Health")
provider.data
```


```{r}

#I made this function that will take the length of the output of the taxonomy by county (I just called it county_collect_NPIcode_taxonomy because it doesn't exist yet) and divides it by the population of the county pulled from census .csv data divided by 1000

providers_per_1000_county <- function(taxonomy, county, state) {
numberprovidersper1000county <- length(county_collect_NPIcode_taxonomy(taxonomy, county))
population <- c()
for (i in length(census)) {
  if (census$STNAME == state) {
    if (census$CTYNAME == county) {
      population <- census$CENSUS2010POP / 1000 {
    }
  }
  }
ratio <- numberprovidersper1000county / population
return(ratio)
}


#other stuff we want to do:
#1) make visualizations for each state
#2) find a way to combine multiple states for a query (i.e. look at #providers/every 1000 people for a few different statess at once)
#3) do this at county level

```{r}

plot<-ggplot(number_practices.low, aes(x=factor(n), y=nn))+
  geom_bar(stat="identity") + labs(x = "Number of providers", y = "Number of zip codes")
print(plot + ggtitle("The number of providers by zipcode"))


```






```