---
title: "Vignette"
output: html_document
---
vignette 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = FALSE)
```

##Introduction to ProvidR
ProvidR is a package that allows you to scrape current NPI data and create streamlined visualizations exploring numbers of providers in the state. This tool can be used to understand both areas with high numbers ofare available and to identify gaps in health care access. 

Some examples of ProvidR uses include: 
-examining providers by taxonomy (i.e. "mental health," "cardiology," "pediatrics")
-exploring provider density by state
-exploring numbers of providers by zip code
-create data visualizations for understanding provider numbers and densities 

##Data in ProvidR
In this package, we have included data from the National Provider Index and the National Census. 

##Functions included in this package
GetDataFromState() creates a data frame with providers from the NPI data base using a given state and provider taxonomy
NumProviderInZip() shows the number of providers in a single zip code for a certain taxonomy
HighProviderNumberZip() allows you to create a bar graph visuzalization of zip codes with the highest number of providers in a given state. 
LowProviderNumberZip() allows you to create a bar graph visualization of the zip codes with the lowest number of providers in a  given state. Zip codes with zero providers are excluded. 
BottomFiveZipcodes() allows you to create a bar graph visualization of the five zip codes with the lowest number of providers (with at least one provider) in a state.
TopFiveZipcodes() allows you to create a bar graph visualization of the five zip codes with the highest number of providers (with at least one provider) in a state.
TopTaxonomiesZip() allows you to output a bar graph of the taxonomy types with the highest numbers of providers in them by zip code. 
BottomTaxonomiesZip() allows you to output a bar graph of the taxonomy types with the lowest numbers of providers in them by zip code. 
ProvidersInStateByCounty() returns a data frame with all of the providers in a state given a taxonomy and breaks them down by county.
SummaryByCounty() this takes the data frame creates with ProvidersInStateByCounty and returns the number of providers in a county, the population of the county, and the number of doctors per 1,000 people. 

##Function examples

<strong>GetDataFromState</strong>
If you give a state and a provider taxonomy, it will input these into the NPI data base and return a data frame with providers within that taxinomical category, in the given state. State should be input as the state abbreviation within quotation marks. Provider taxonomy should also be input in quotation marks. 
```{r}
GetDataFromState("RI", "Mental Health")
```

<strong>NumProviderInZip</strong>
This function allows you to determine the number of providers in a zipcode given a specific taxonomy (such as Mental Health, Primary Care...)
```{r}
NumProviderInZip("02906", "Mental Health")
```


#Customizable Visualizations

<strong>HighProviderNumberZip()</strong>
This function allows you to output a visualization of the zip codes with the highest number of providers in a state. It takes the argument HighProviderNumberZip(data) to show the zip codes with the highest number of providers in a bar graph.
```{r}
data<-GetDataFromState("RI","mental health")
HighProviderNumberZip(data)
```

<strong>LowProviderNumberZip()</strong>
This function allows you to output a visualization of the zip codes with the lowest number of providers in a state (with at least one provider minimum in the zip code). It takes the argument HighProviderNumberZip(data) to show the zip codes with the lowest number of providers in a bar graph.
```{r}
data<-GetDataFromState("RI","mental health")
LowProviderNumberZip(data)
```

<strong>BottomFiveZipcodes()</strong>
This function allows you to output a visualization of the five zip codes with the lowest number of providers (with at least one provider) in a state in a bar graph.
```{r}
data<-GetDataFromState("RI","mental health")
BottomFiveZipcodes(data)
```

<strong>TopFiveZipcodes()</strong>
This function allows you to output a visualization of the five zip codes with the highest number of providers in a state in a bar graph.
```{r}
data<-GetDataFromState("RI","mental health")
TopFiveZipcodes(data)
```

<strong>TopTaxonomiesZip()</strong>
This function allows you to output a visualization of the taxonomy types with the highest numbers of providers in them by zip code. 
```{r}
data<-GetDataFromState("RI","mental health")
TopTaxonomiesZip(data)
```

<strong>BottomTaxonomiesZip()</strong>
This function allows you to output a visualization of the taxonomy types with the highest numbers of providers in them by zip code. 
```{r}
data<-GetDataFromState("RI","mental health")
BottomTaxonomiesZip(data)
```


<strong>BottomFiveProviderDensities</strong>
This function allows you to output a visualization of the bottom five lowest provider densities in a state given a taxonomy. 
```{r}
data<-SummaryByCounty<-function(state, taxonomy)
BottomFiveProviderDensities(data)
```
  
<strong>TopFiveProviderDensities</>
This function allows you to output a visualization of the top five highest provider densities in a state given a taxonomy. 
```{r}
data<-SummaryByCounty<-function(state, taxonomy)
TopFiveProviderDensities(data)
```

<strong>ProvidersInStateByCounty</strong>
This function retrns a data frame that includes the providers in a state, given a provider taxonomy, by county.
```{r}
ProviderInStateByCounty("RI", "Primary Care")
```

<strong>SummaryByCounty</strong>
This returns the number of providers in a county, the population of the county and the number of providers per 1,000 county residents. 
```{r}
SummaryByCounty("RI", "Primary Care")
```

<strong>DensityMapByCounty</strong>
This plots a heatmap of the provider density in each county in  the state.
```{r}
DensityMapByCounty("RI","Primary Care")
```
